Evaluation of Diagnostic Concordance Between Algorithms for Parkinson’s Disease Dementia

### 2025-09-23 _manuscript/manuscript.qmd
Tidying the code.

dates <- sapply(
  c("min", "max"), function(f) {
    date <- do.call(f, list(data$assdate))
    paste(month(date, label = T, abbr = F), year(date))
  }
)
```

@@

critnum <- sapply(
  c("mmse", "moca", "smoca", "lvlII"), function(i) {
    subset(crit, group == i) |>
      nrow()
  }
)

@@

# In-text rate estimates
rates_overall <- sapply(c("M", "SD", "Md", "minmax"), function(f) do_summary(perc, 2, f))
rates_FAQ9 <- sapply(c("M", "SD", "Md", "minmax"), function(f) do_summary(perc[grepl("FAQ 9", rates$table$IADL)], 2, f))
rates_FAQtot <- sapply(c("M", "SD", "Md", "minmax"), function(f) do_summary(perc[rates$table$IADL == "FAQ > 7"], 2, f))

@@

# Prepare combinations within IADL operationalisation:
kappas <- lapply(
  set_names(names(algos)), function(o) {
    combn(algos[[o]], 2) |>
      t() |>
      as_tibble() |>
      `colnames<-`(c("predictor", "reference")) |>
      left_join(conc$table, by = c("predictor", "reference")) |>
      select(Kappa_raw) |>
      pull()
  }
)

@@

# Extract Kappa summaries:
kappa_sums <-
  sapply(
    names(kappas),
    function(i)
      paste0(do_summary(kappas[[i]], 2, "M"),", SD = ", do_summary(kappas[[i]], 2, "SD"))
  )

# Add Kappa summaries of algos with same everything but different IADL:
kappa_iadl <-
  data.frame(
    predictor = c("Lvl.II (1)", "MMSE (1)", "MMSE (3)", paste0("MoCA (",seq(1,59,2),")"), "sMoCA (1)"),
    reference = c("Lvl.II (2)", "MMSE (2)", "MMSE (4)", paste0("MoCA (",seq(2,60,2),")"), "sMoCA (2)")
  ) |>
    left_join(conc$table) |>
    select(Kappa_raw) |>
    pull()

>>>>

dates <- sapply(c("min", "max"), function(f) {
  date <- do.call(f, list(data$assdate))
  paste(month(date, label = TRUE, abbr = FALSE), year(date))
})
```

@@

critnum <- sapply(c("mmse", "moca", "smoca", "lvlII"), function(i) {
  subset(crit, group == i) |>
    nrow()
})

@@

# In-text rate estimates
rates_overall <- sapply(c("M", "SD", "Md", "minmax"), \(f) do_summary(perc, 2, f))
rates_FAQ9 <- sapply(c("M", "SD", "Md", "minmax"), \(f) do_summary(perc[grepl("FAQ 9", rates$table$IADL)], 2, f))
rates_FAQtot <- sapply(c("M", "SD", "Md", "minmax"), \(f) do_summary(perc[rates$table$IADL == "FAQ > 7"], 2, f))

@@

# Prepare combinations within IADL operationalisation:
kappas <- lapply(set_names(names(algos)), function(o) {
  combn(algos[[o]], 2) |>
      t() |>
      as_tibble() |>
      `colnames<-`(c("predictor", "reference")) |>
      left_join(conc$table, by = join_by(predictor, reference)) |>
      pull(Kappa_raw)
})

@@

# Extract Kappa summaries:
kappa_sums <- sapply(names(kappas), function(i) {
  paste0(do_summary(kappas[[i]], 2, "M"),", SD = ", do_summary(kappas[[i]], 2, "SD"))
})

# Add Kappa summaries of algos with same everything but different IADL:
kappa_iadl <- data.frame(
  predictor = c("Lvl.II (1)", "MMSE (1)", "MMSE (3)", paste0("MoCA (",seq(1,59,2),")"), "sMoCA (1)"),
    reference = c("Lvl.II (2)", "MMSE (2)", "MMSE (4)", paste0("MoCA (",seq(2,60,2),")"), "sMoCA (2)")
) |>
  left_join(conc$table) |>
  pull(Kappa_raw)
